Modular flow and holographic entanglement entropy in cutoff AdS

### 2021-06-05 alpha/CutoffModularFlow/draft1.tex
Rename alpha document to draft

	\sidenote{One oddity of this prescription is that the codim-1 cutoff geometry depends on the choice of the interval $\mcal{A}$}. This seems to suggest that there is no canonical way to embed the entire time-evolved deformed field theory into the bulk. The best we can do is to embed the causal diamond $\mcal{D}(\mcal{A})$ (\sidenote{and maybe $\mcal{D}(\mcal{A})$}), given an interval $\mcal{A}$. This is the price we have to pay for SSA to hold.

>>>>

	\sidenote{One oddity of this prescription is that the codim-1 cutoff geometry depends on the choice of the interval $\mcal{A}$}. This seems to suggest that there is no canonical way to embed the entire time-evolved deformed field theory into the bulk. The best we can do is to embed the causal diamonds $\mcal{D}(\mcal{A}) \cup \mcal{D}(\bar{\mcal{A}})$, given an interval $\mcal{A}$ and its complement $\bar{\mcal{A}}$. This is the price we have to pay for SSA to hold.
